Paper Report "MacroBase: Prioritizing Attention in Fast Data" \\ Big Data Storage and Processing Infrastructures

### 2019-03-19 paper-report.tex
close

		In this report I am going to summarize and explain the paper "\textit{MacroBase}: Prioritizing Attention in Fast Data". I am going to explain the main concept and description of \textit{MacroBase}, the design behind it, the tests the researchers did on the solution, their conclusions and finally I will link it with the IBD course and expose my conclusions gathered after reading the paper.

@@

		As stated before, \textit{MacroBase} prioritizes attention and to do so it uses two classes of operators: Classification operators, which examine data points and labels them according to user-specified classes, and Explanation operators which will group and aggregate multiple data points. Developing these operators is the core concept behind \textit{MacroBase}, relational analytics have well defined re-usable operators but not for classification and explanation. With this in mind, the paper explained \textit{MicroBase} structure and architecture the following way.

@@

		\\\textbf{4. Explanation.} Instead of returning the result of labelled points, \textit{MacroBase} will aggregate them and create explanations. By default, \textit{MicroBase} will return explanations in the form of attribute-value combinations common among outlier points and uncommon among inlier points. This operator will receive a stream of labelled points (\textit{Label, Point}) and will generate explanations (\textit{Explanation}). The \textit{Explanation} subclass provide additional information like statistics or representative sequences of points. \textit{MicroBase} will continuously execute explanation operators to summarize the stream, but the emission of explanations will be done by user demand to avoid waste of resources.
		\\\textbf{5. Presentation.} Given that the number of generated explanations may still be large, \textit{MicroBase} pipelines rank explanations by statistics specific to the explanations and sorts them by their degree of outlier. By default, \textit{MicroBase} will render a report and present it via REST API or GUI.

@@

@@

\end{document}

>>>>

		In this report I am going to summarize and explain the paper "\textit{MacroBase}: Prioritizing Attention in Fast Data". I am going to explain the main concept and description of \textit{MacroBase}, the design behind it, the tests the researchers did on the solution, comment their results and finally I will link it with the IBD course and expose my conclusions gathered after reading the paper.

@@

		As stated before, \textit{MacroBase} prioritizes attention and to do so it uses two classes of operators: Classification operators, which examine data points and labels them according to user-specified classes, and Explanation operators which will group and aggregate multiple data points. Developing these operators is the core concept behind \textit{MacroBase}, relational analytics have well defined re-usable operators but not for classification and explanation. With this in mind, the paper explained \textit{MacroBase} structure and architecture the following way.

@@

		\\\textbf{4. Explanation.} Instead of returning the result of labelled points, \textit{MacroBase} will aggregate them and create explanations. By default, \textit{MacroBase} will return explanations in the form of attribute-value combinations common among outlier points and uncommon among inlier points. This operator will receive a stream of labelled points (\textit{Label, Point}) and will generate explanations (\textit{Explanation}). The \textit{Explanation} subclass provide additional information like statistics or representative sequences of points. \textit{MacroBase} will continuously execute explanation operators to summarize the stream, but the emission of explanations will be done by user demand to avoid waste of resources.
		\\\textbf{5. Presentation.} Given that the number of generated explanations may still be large, \textit{MacroBase} pipelines rank explanations by statistics specific to the explanations and sorts them by their degree of outlier. By default, \textit{MacroBase} will render a report and present it via REST API or GUI.

@@

		Although \textit{MacroBase} lets users to configure their own operators, they also offer default classification operators. In the paper they explain how the estimation procedure and the streaming execution is designed.
		\\\textbf{1. Robust Estimation Procedure.} \textit{MacroBase} uses unsupervised density-based classification to identify points that abnormal relative to the population, but as the paper states some anomalous points can impact on density estimation with calculations such as \textit{Z-Score}. To solve this problem \textit{MacroBase} Default Pipeline (MDP) uses the following robust estimation calculations: the Median Absolute Deviation (MAD) for univariate data since the median is resistant to outliers and the Minimum Covariance Determinant (MCD) for multivariate data that finds the tightest points that represent the sample and summarizes them with their location and scatter. These unsupervised models allow MDP to score points without requiring labels or rules from users and in the paper they clearly show these procedures are way more robust than the \textit{Z-Score}.
		\\\textbf{2. MDP Streaming Execution.} The procedures explained before, although robust, are not prepared for an streaming context in which they must be retrained over a continuous stream of data. For this problem, \textit{MacroBase} uses the Adaptable Damped Reservoir (ADP) which maintains a sample of input data that is exponentially weighted towards more recent points and also operates over window sizes enabling flexibility. The probability of inserting a point in this window is an exponentially weighting function of the number of points observed so far, while the decay of points may depend on the users application and/or workload. For this reason, \textit{MacroBase} supports two decay policies: time-based decay which decays at a specified rate measured according to real time and batch-based decay which decays at a specified rate measured by arbitrarily sized batches. With this implementation \textit{MacroBase} solves the problem of maintaining training inputs and maintaining percentile thresholds.

@@

	\section{MacroBase Default Pipeline Explanation}
		As explained above, \textit{MacroBase} uses explanations to contextualize and differentiate outliers and inliers according to their attributes. In this paper they explain how to achieve this,  what is the explanation strategy and how to implement it in streaming.
		\\\textbf{1. Risk Ratio} or relative risk ratio, is an epidemiology metric used in the MDP to identify combinations of attribute values that are relatively common in outliers. This metric quantifies how much more likely a data point is to be an outlier if it is of a specific attribute combination, as opposed to the general population. MDP finds combinations with high support or occurrence and, for this purpose, it accepts a minimum risk ratio and level of outlier support as input parameter.
		\\\textbf{2. Basic Explanation Strategy} As the paper states, the first solution to apply risk ratio for several attribute sets is to search twice but this is a waste of time and effort. To solve this, MDP exploits the cardinality imbalance that reduces the attributes to explore and also takes advantage of individual item ratios computing them first as these are cheap or inexpensive and then the combinations. The final strategy is as follows: MDP calculates the attribute values with minimum risk ratio, then computes the supported outlier attribute combinations and finally computes the risk ratio for each combination based on their support in the inliers.
		\\\textbf{3. Streaming Explanation.} They state in the paper that individual attributes have enough characteristics to support counts. To count individual attributes frequent items the MDP uses a heavy-hitters sketch called Amortized Maintenance Counter (AMC). However MDP also needs to track combinations of attributes and, for that, they developed a combination of data structures: AMC for the frequent attributes and an adaptation of the CPS-Tree data structure to store frequent attributes. To sum up the whole explanation streaming process, when a data point arrives at this summarization operator, \textit{MacroBase} inserts each point's attributes into an AMC sketch, then inserts a subset of point's attributes into a tree that maintains a frequency descending order and when the window elapses, \textit{MacroBase} decays the count of the items and the counts in each node of the prefix tree, removes the attributes that are no longer above the support threshold and rearranges the prefix tree order.
	\section{Evaluation}

	\end{flushleft}
\end{document}
